\documentstyle[margin,line,hyperref]{res}

\raggedright

\newenvironment{listitems}{
  \begin{list}{$\bullet$}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in} 
      \setlength{\leftmargin}{0.2in}}}{\end{list}}

\hypersetup{pdfpagemode=FullScreen, colorlinks=false}

% Macros -- for abbrevs etc
% \def\Cplusplus{{\rm C\raise.5ex\hbox{\small ++}}}
% \def\first{{\raise.5ex\hbox{\small st}}}
% \def\second{{\raise.5ex\hbox{\small nd}}}
% \def\third{{\raise.5ex\hbox{\small rd}}}
% \def\fourth{{\raise.5ex\hbox{\small th}}}

\setlength{\oddsidemargin}{-0.5in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textwidth}{6.0in}
\setlength{\headheight}{0.0in}
\setlength{\topmargin}{-0.1in}
\setlength{\textheight}{9.75in}

\renewcommand{\namefont}{\LARGE\sc\bf}

\begin{document}
\name{\sc{\bf{Guy Haskin Fernald, Ph.D.}}}

% \address{
%   1 Main Street
%   MyTown, MYSTATE 11111
% }
% \address{
%   \texttt{none@none.com} \\
%   \small{
%   \href{http://www.none.com/}{http://www.none.com/}
%   }
% }

\begin{resume}

% \section{\sc{Contact Information}}
% \begin{tabular}{@{}p{2in}p{4in}}
% 1 Main Street                 & \emph{Web:} \href{http://www.none.com/}{www.none.com} \\
% My Town, MYSTATE, 1111        & \emph{Email:}  \href{mailto:none@none.com}{none@none.com}
                               %& \emph{Voice:}  (111) 111-1111 \\
                               %& \emph{Fax:}    (111) 111-1111 \\
% \end{tabular}


\section{\sc{Interests}}
Data science, machine learning, biomedical informatics, drug repositioning, and drug discovery.


\section{\sc{Professional Experience}}
\begin{format}
  \employer{l}\location{r}\\
  \title{l}\dates{r}\\
  \body\\
\end{format}


\employer{\textbf{Foresite Labs}}
\title{\small{\sc{Staff Data Scientist}}}
\location{\textit{San Francisco, California}}
\dates{\textbf{2018 -- present}}
\begin{position}
At Foresite I am building data pipelines and developing novel machine learning methods that aggregate and integrate large-scale genomic, biological and pharmacological datasets to identify and incubate investment opportunities in biomedicine.
\end{position}

\vspace{-0.5em}

\employer{\textbf{Vium}}
\title{\small{\sc{Data Scientist, Researcher, Developer}}}
\location{\textit{San Mateo, California}}
\dates{\textbf{2016 -- 2018}}
\begin{position}
Designing and developing novel metrics, algorithms, and statistical methods for a cloud-based software system.  Writing production software, implementing machine learning methods, and authoring tools to analyze pre-clinical data from drug studies using large data sets generated from high-volume, continuously monitored sensors.
\end{position}

\vspace{-0.5em}


\employer{\textbf{Tech Consultant and Developer}}
\title{\small{\sc{Data Scientist, Developer}}}
\location{\textit{San Francisco, California}}
\dates{\textbf{2015}}
\begin{position}
Investigated commercial applications of biomedical research. Developed software using R, Python, and AWS to analyze biological and chemical data sets and create pipelines to enable and support drug discovery.  Performed due diligence and invested in tech and biotech startups.
\end{position}

\vspace{-0.5em}

\employer{\textbf{Stanford University}}
\title{\small{\sc{Graduate Researcher and Instructor}}}
\location{\textit{Stanford, California}}
\dates{\textbf{2007 -- 2014}}
\begin{position}
Conceived and conducted original research ideas, developed software in R and Python on a cluster and using AWS.
Analyzed and investigated hypotheses on large scale biomedical, genetic, and chemical datasets.
Taught and mentored students in bioinformatics and data analysis.
Coordinated and collaborated with external research groups.
\end{position}



\employer{\textbf{University of California, San Francisco}}
\title{\small{\sc{Research Associate}}}
\location{\textit{San Francisco, California}}
\dates{\textbf{2004 -- 2007}}
\begin{position}
Investigated the role of genetic linkage and gene expression in multiple sclerosis and experimental autoimmune encephalomyelitis through statistical methods, network analysis, and computer modeling.
\end{position}


\vspace{-0.5em}
\employer{\textbf{Instituto Nacional de Salud P\'{u}blica}\\
\small{(National Public Health Institute)}}
\title{\small{\sc{Technical Consultant}}}
\location{\textit{Cuernavaca, M\'{e}xico}}
\dates{\textbf{2001 -- 2003}}
\begin{position}
Developed direction and managed the implementation of internal and external computer resources for the health economics group.  Worked in Spanish and English.
\end{position}


\vspace{-0.5em}
\employer{\textbf{Ariba} \small{(acquired by SAP)}}
\title{\small{\sc{Manager and Engineer}}}
\location{\textit{Sunnyvale, California}}
\dates{\textbf{1996 -- 2001}}
\begin{position}
Member of original technical team that developed patented purchasing system.  Worked on first six versions of released software. Managed team of programmers that implemented internationalization, management tools, and web applications.
\end{position}

\vspace{-0.5em}
\employer{\textbf{Netmarket} \small{(acquired by Trilegiant)}}
\title{\small{\sc{Founder and Chief Programmer}}}
\location{\textit{Cambridge, Massachusetts}}
\dates{\textbf{1993 -- 1996}}
\begin{position}
Co-founded software startup, hired engineers, and led software development efforts. Wrote software for first music CD store on the web, as featured in the \href{http://select.nytimes.com/gst/abstract.html?res=FA0F1FFA3E540C718DDDA10894DC494D81}{New York Times}.
\end{position}

% \employer{\textbf{Swarthmore College}}
% \title{\small{\sc{System Administrator}}}
% \location{\textit{Swarthmore, Pennsylvania}}
% \dates{\textbf{1993 -- 1994}}
% \begin{position}
% Responsible for maintenance of Sun Computers, hardware, software, user support.
% \end{position}

% \employer{\textbf{Swarthmore College}}
% \title{\small{\sc{Summer Researcher, Computer Science}}}
% \location{\textit{Swarthmore, Pennsylvania}}
% \dates{\textbf{1993}}
% \begin{position}
% Investigated the use of diagrams in developing proof plans for a natural deduction system.
% \end{position}

% \employer{\textbf{Nasa Ames Research Center}}
% \title{\small{\sc{Graphics Programmer}}}
% \location{\textit{Moffet Field, California}}
% \dates{\textbf{1990}}
% \begin{position}
% Conceived and produced animations and images for turbomachinery research group.
% \end{position}

\section{\sc{Patents}}
Adams N, Brown M, Carlstrom B, Elkin B, Hegarty P, \underline{Haskin G}, Putanec B. Operating resource management system.  \href{http://patft.uspto.gov/netacgi/nph-Parser?Sect1=PTO1&Sect2=HITOFF&d=PALL&p=1&u=%2Fnetahtml%2FPTO%2Fsrchnum.htm&r=1&f=G&l=50&s1=7117165.PN.&OS=PN/7117165&RS=PN/7117165}{US Patent no. 7,117,165, October 3, 2006}.

Tatonetti N, Altman R,  \underline{Fernald G Haskin}. Signal Detection Algorithms to Identify Drug Effects and Drug Interactions.  Patent pending. \href{http://appft1.uspto.gov/netacgi/nph-Parser?Sect1=PTO1&Sect2=HITOFF&d=PG01&p=1&u=/netahtml/PTO/srchnum.html&r=1&f=G&l=50&s1=20160217395.PGNR.&OS=DN/20160217395&RS=DN/20160217395}{US Patent Application July 28, 2016}

\section{\sc{Education}}
\begin{format}
  \employer{l}\location{r}\\
  \body\\
\end{format}

\employer{\textbf{Stanford University}, \textit{Stanford, CA}}
\location{\hspace{0.25in}\textbf{2007 -- 2014}}
\title{}
\dates{}
\begin{position}
\vspace{1.5em}
\begin{listitems}

\item \textbf{Ph.D. and M.S. in Biomedical Informatics}.  Dissertation:
    \textit{Connecting chemical features of drugs to molecular, cellular, and
    organismal phenotypes}.  Funded by NIH LM07033 and R24GM61374. Coursework included
    translational medicine, genetics, pharmacogenomics, and biostatisics.

\item \textbf{M.S. in Medicine}.  Howard
    Hughes Medical Institute training program for translational medicine.  Coursework covered
    the first two years of a Medical Degree including anatomy, physiology,
    immunology, pathology, and human health and disease.

\end{listitems}
\end{position}

%\employer{\textbf{UC Berkeley Extension}}
%\location{\textit{Berkeley, California}\hspace{0.25in}\textbf{2004}}
%\title{}
%\dates{}
%\begin{position}
%Classes in microbiology and bioinformatics.
%\end{position}
%
%
%\employer{\textbf{City College of San Francisco}}
%\location{\textit{San Francisco, California}\hspace{0.25in}\textbf{2003}}
%\title{}
%\dates{}
%\begin{position}
%Classes in biology and chemistry.  Laboratory work in PCR, recombinant DNA, and gel electrophoresis.
%\end{position}

\employer{\textbf{Swarthmore College}, \textit{Swarthmore, PA}}
\location{\hspace{0.25in}\textbf{1990 -- 1994}}
\title{}
\dates{}
\begin{position}
\vspace{1.5em}
\begin{listitems}

    \item \textbf{B.A. in Mathematics and Computer Science}.  Additional courses at the University of Edinburgh.

\end{listitems}
\end{position}

% \vspace{-1em}


\section{\sc{Publications}}
\raggedright

Karczewski, KJ, \underline{Fernald, GH}, et al. STORMSeq: an open-source, user-friendly pipeline for processing personal genomics data in the cloud. \href{http://www.ncbi.nlm.nih.gov/entrez/query.fcgi?db=pubmed&cmd=Retrieve&dopt=AbstractPlus&list_uids= 24454756}{PLoS One 2014, 9(1):e84860.}

\underline{Fernald GH} and Altman RB.  Using molecular features of xenobiotics to predict hepatic gene expression response.  \href{http://www.ncbi.nlm.nih.gov/entrez/query.fcgi?db=pubmed&cmd=Retrieve&dopt=AbstractPlus&list_uids=24010729}{J Chem Inf Model. Sep 6. 2013 Oct 28;53(10):2765-73).}

Tatonetti NP, \underline{Fernald GH}, and Altman RB. A novel signal detection algorithm for identifying hidden drug-drug interactions in adverse event reports.
\href{http://www.ncbi.nlm.nih.gov/entrez/query.fcgi?db=pubmed&cmd=Retrieve&dopt=AbstractPlus&list_uids=21613990}{J Am Med Inform Assoc. 2012 Jun 14.}

\underline{Fernald GH}, Capriotti E, Daneshjou R, Karczewski KJ,
Altman RB.  Bioinformatics Challenges for Personalized Medicine.
\href{http://www.ncbi.nlm.nih.gov/entrez/query.fcgi?db=pubmed&cmd=Retrieve&dopt=AbstractPlus&list_uids=21596790}{Bioinformatics (2011) 27 (13): 1741-1748.}

Tatonetti NP, Denny JC, Murphy SN, \underline{Fernald GH}, Krishnan G, Castro V, Yue P, Tsau PS, Kohane I, Roden DM, and Altman RB.
Detecting drug interactions from adverse-event reports: interaction between paroxetine and pravastatin increases blood glucose levels.
\href{http://www.ncbi.nlm.nih.gov/entrez/query.fcgi?db=pubmed&cmd=Retrieve&dopt=AbstractPlus&list_uids=21613990}{Clinical Pharmacology and Therapeutics (2011) 90 1, 133-142.}

Han MH, Hwang SI, Roy DB, Lundgren DH, Price JV, Ousman SS, \underline{Fernald GH}, Gerlitz B, Robinson WH, Baranzini SE, Grinnell BW, Raine CS, Sobel RA, Han DK, Steinman L. Proteomic analysis of active multiple sclerosis lesions reveals therapeutic targets. \href{http://www.ncbi.nlm.nih.gov/entrez/query.fcgi?db=pubmed&cmd=Retrieve&dopt=AbstractPlus&list_uids=18278032}{Nature. 2008 Feb 28;451(7182):1076-81}.

\underline{Fernald GH}, Pachner A, Caillier S, Narayan K, Oksenberg JR, Baranzini SE.  Genome-Wide Network Analysis Reveals the Global Properties of IFN-beta Immediate Transcriptional Effects in Humans.\href{http://www.ncbi.nlm.nih.gov/entrez/query.fcgi?db=pubmed&cmd=Retrieve&dopt=AbstractPlus&list_uids=17404290}{J Immunol. 2007 Apr 15;178(8):5076-85}.

\underline{Fernald GH}, Yeh RF, Hauser SL, Oksenberg JR, Baranzini SE. 2005. Mapping gene activity in complex disorders: Integration of expression and genomic scans for multiple sclerosis. \href{http://www.ncbi.nlm.nih.gov/entrez/query.fcgi?db=pubmed&cmd=Retrieve&dopt=AbstractPlus&list_uids=16129498}{J Neuroimmunol 167(1-2):157-69}.


% \section{\sc{Conference Presentations}}

% \underline{Fernald GH}, Altman RB.  2012.  Supervised Machine Learning Analysis of Drug Induced Gene Expression, National Library of Medicine Informatics Training Conference.  Madison, WI.

% \underline{Fernald GH}, Tatonetti NP, Altman RB.  2010.  A Systems Biology
% Method for Predicting Drug-Gene Interactions in Saccharomyces
% cerevisiae, P-STAR Conference, Memphis, TN. 

% \underline{Fernald GH}, Pachner A, Caillier S, Narayan K, Oksenberg JR, Baranzini SE.  2006. Network-based analysis unveils global properties of IFN$\beta$ immediate transcriptional effects in humans. International Conference on Complex Systems. Boston, Massachusetts.

% \section{\sc{Poster Presentations}}

% \underline{Fernald GH}, Tatonetti NP, Altman RB.
% Generating Credible Hypotheses for Drug-Drug and Drug-Gene Phenotypes.
% NLM Bioinformatics Training Program Conference, June 2011.

% \underline{Fernald GH}, Tatonetti NP, Altman RB.
% A Systems Biology Method for Predicting Drug-Gene Interaction in
% Saccharomyces cerevisiae.  BCATS 2010.

% \underline{Fernald GH}, Tatonetti NP, Altman RB. PharmReduce: A
% Symmetric Framework to Rank Pharmacogenes, Phenotypic Effects, and
% Small Molecules. BCATS 2009.

\section{\sc{Honors and Awards}}
\begin{listitems}
\item National Science Foundation GRFP Honorable Mention, 2009.
\item National Library of Medicine Training Grant Recipient, 2008.
\item Phi Beta Kappa, 1994.
\item Bachelor of Arts awarded with Distinction, 1994.
% \item Nasa Ames Group Achievement Award, 1990.
\end{listitems}

\section{\sc{Technical Skills}}
\begin{listitems}
\item{Programming Experience: statistical computing, client/server database, distributed computing.}
\item{Languages:  Python, R, Scala, Spark, SQL, HTML5, CSS3, C, Ruby, Perl, MATLAB, \LaTeX{}.}
\item{Platforms: AWS, GCP, Unix (Linux, Solaris, OS X), Windows.}
\end{listitems}

\section{\sc{Interests and Skills}}
\begin{listitems}
\item Activities and skills: Spanish language, cooking (Certificate
  in Culinary Arts from the French Culinary Institute, New York City), classical
  guitar, and tennis.
\item Board member: San Francisco Works (previous), Mission Learning
  Center (previous).
\end{listitems}

%\vspace{.25in}

%\section{\sc{References}}
%Available on request.

\end{resume}
\end{document}
